\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-11-29 smurf_paper.tex
add newer/better reference for BoA

Iterative approaches to map-making have a long history in the
submillimetre, such as the pipeline recipe for fitting and removing
baseline drifts in SCUBA scan-map data as the astronomical image
estimate improved \citep{1999ASPC..172..171J}. The closest modern
relatives are the Comprehensive Reduction Utility
\citep[CRUSH,][]{kovacs2008} for the Submillimeter High-Angular
Resolution Camera 2 (SHARC-2), the Bolometer array data Analysis
software (BoA) for the Large APEX BOlometer CAmera
\citep[LABOCA,][]{siringo2009}, and the pipeline developed for the
Bolocam Galactic Plane Survey \citep{aguirre2011}.

@@

This paper has described the Submillimetre User Reduction Facility
(SMURF), which was designed to produce maps from the rapidly sampled
$\sim10^4$ bolometers of the \scuba\ instrument. While similar to
other algorithms in the literature that iteratively model and remove
correlated noise components from the data, successively improving the
map \citep[e.g.,][]{kovacs2008,siringo2009,aguirre2011}, we have shown
that a relatively simpler approach provides good results for \scuba\
data, with reasonable computational requirements. This conclusion is
encouraging for the development of future large-format bolometer
arrays, for which our specific approach should be useful when even
larger volumes of data are involved.

>>>>

Iterative approaches to map-making have a long history in the
submillimetre, such as the pipeline recipe for fitting and removing
baseline drifts in SCUBA scan-map data as the astronomical image
estimate improved \citep{1999ASPC..172..171J}. The closest modern
relatives are the Comprehensive Reduction Utility
\citep[CRUSH,][]{kovacs2008} for the Submillimeter High-Angular
Resolution Camera 2 (SHARC-2), the pipeline developed for the Bolocam
Galactic Plane Survey \citep{aguirre2011}, and the Bolometer array
data Analysis software (BoA) for the Large APEX BOlometer CAmera
\citep[LABOCA,][]{schuller2012}.

@@

This paper has described the Submillimetre User Reduction Facility
(SMURF), which was designed to produce maps from the rapidly sampled
$\sim10^4$ bolometers of the \scuba\ instrument. While similar to
other algorithms in the literature that iteratively model and remove
correlated noise components from the data, successively improving the
map \citep[e.g.,][]{kovacs2008,aguirre2011,schuller2012}, we have shown
that a relatively simpler approach provides good results for \scuba\
data, with reasonable computational requirements. This conclusion is
encouraging for the development of future large-format bolometer
arrays, for which our specific approach should be useful when even
larger volumes of data are involved.
